Automatic Medical Coding for Neonatal Jaundice with Machine Learning

### 2018-04-29 paper/paper.tex
Added to document representation

Finally, collocations, or common multiword phrases, are detected and replaced with a single token. In order to automatically detect collocations in our corpus, we calculate the \textit{normalized pointwise mutual information} (NPMI) of every pair of words in the corpus [BOUMA]. The NPMI is given by \eqref{pmi}, where $x$ and $y$ are indicators for a two given words appearing in text, $p(x,y)$ is the probability of the two words appearing next to each other, and all probabilities are measured empirically from our corpus.
\begin{equation}
i_n(x,y) = \frac{-1}{\ln p(x,y)}\ln \frac{p(x,y)}{p(x)p(y)}\label{pmi}
\end{equation}
Intuitively, NMPI measures how much the the co-occurance of two words $x$ and $y$ differs from what we would expect if their occurrences were independent of each other. For word pairs in our corpus with high NMPI, we normalized co-occurances in raw text into a single token (see Table~\ref{reptab}).
\subsection{Document Representation}\label{AA}

\subsection{Classification Models}\label{AA}

@@

Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

@@

\section{Conclusion}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

>>>>

Finally, collocations, or common multiword phrases, are detected and replaced with a single token. In order to automatically detect collocations in our corpus, we calculate the \textit{normalized pointwise mutual information} (NPMI) of every pair of words in the corpus [BOUMA]. The NPMI is given by \eqref{pmi}, where $x$ and $y$ are indicators for a two given words appearing in text, $p(x,y)$ is the probability of the two words appearing next to each other, and all probabilities are measured empirically from our corpus.
\begin{equation}
i_n(x,y) = \frac{-1}{\ln p(x,y)}\ln \frac{p(x,y)}{p(x)p(y)}\label{pmi}
\end{equation}
Intuitively, NMPI measures how much the the co-occurance of two words $x$ and $y$ differs from what we would expect if their occurrences were independent of each other. For word pairs in our corpus with high NMPI, we normalized co-occurances in raw text into a single token (see Table~\ref{reptab}).
\subsection{Document Representation}\label{AA}
In order to classify notesets, we have to represent them as vectors. While deeper methods (e.g. convolutional neural networks) are able to take word order into account, we choose to use a \textit{bag-of-words} (BoW) model in which we ignore the actual ordering of words in a document and instead simply count the number of occurrences of each unique word in the document. This has the benefit of greatly simplifying our document representation, but it throws away potentially valuable information contained in word ordering (e.g. "negative for cancer, positive for flu" and "positive for cancer, negative for flu" will have the same BoW representation). Despite this disadvantage, however, BoW representations work very well in practice for many applications.

A naive approach to BoW representation is a \textit{count vector}. In a count vector, 
\subsection{Classification Models}\label{AA}

@@

@@

\section{Conclusion}
